Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-09 manuscript/paper.Rmd
table

@@

vars %>% kable(booktabs = T) %>% kable_styling(latex_options = "scale_down")

>>>>

| Variable | Name                    | Description                                                                                                                                  |
|-------------|---------------|---------------------------------------------|
| SEQN     | sequence number         | Respondent number                                                                                                                            |
| SDMVPSU  | psu                     | Masked variance unit pseudo-PSU variable for variance estimation                                                                             |
| WTINT2YR | weights                 | Full sample 2-year interview weights                                                                                                         |
| SDMVSTRA | strata                  | Masked variance unit pseudo-stratum variable for variance estimation                                                                         |
| RIAGENDR | gender                  | Respondent's number                                                                                                                          |
| RIDAGEYR | age (yrs)               | Respondent's age in years                                                                                                                    |
| DMDMARTL | marital status          | Marital status                                                                                                                               |
| INDFMIN2 | income category         | Total family income (reported as a range value in dollars)                                                                                   |
| RIDRETH3 | race                    | Recode of reported race and Hispanic origin information, with Non-Hispanic Asian Category                                                    |
| DMDHHSZA | children \<5            | Number of children aged 5 years or younger in the household                                                                                  |
| DMDEDUC2 | education level         | What is the highest grade or level of school {you have/SP has} completed or the highest degree {you have/s/he has} received?                 |
| DMDCITZN | citizenship status      | {Are you/Is SP} a citizen of the United States? [Information about citizenship is being collected by the U.S. Public Health Serv             |
| SLD012   | sleep                   | Number of hours usually sleep on weekdays or workdays                                                                                        |
| BMXBMI   | bmi                     | Body mass index                                                                                                                              |
| ALQ121   | alcohol use             | In the past 12 months, how often did you drink any type of alcoholic beverage?                                                               |
| LBDHDDSI | hdl                     | High density lipoprotein                                                                                                                     |
| LBDSALSI | albumin                 | Albumin (g/L)                                                                                                                                |
| DIQ010   | diabetes                | Have you ever been told by a doctor or health professional that you have diabetes or sugar diabetes?                                         |
| BPQ020   | hypertension            | {Have you/Has SP} ever been told by a doctor or other health professional that {you/s/he} had hypertension, also called high blood pressure? |
| URXCRS   | creatinine              | Creatinine, urine (umol/L)                                                                                                                   |
| SLQ040   | snort                   | In the past 12 months, how often did {you/SP} snort, gasp, or stop breathing while {you were/s/he was} asleep?                               |
| LBDTCSI  | total cholestrol levels | Total cholesterol (mmol/L)                                                                                                                   |
| LBXHGB   | hemoglobin              | Hemoglobin (g/dL)                                                                                                                            |
| LBXSASSI | AST                     | Aspartate aminotransferase                                                                                                                   |
| SMQ040   | smoke                   | Do you now smoke cigarettes?                                                                                                                 |
| BPXDI    | blood pressure          | Systolic and diastolic blood pressure taken as the average of the first three measurements                                                   |

@@

#vars %>% kable(booktabs = T) %>% kable_styling(latex_options = "scale_down")
